\newglossaryentry{GOAL}
{
  name=GOAL,
  description={"GOAL is an agent programming language for programming rational agents. GOAL agents derive their choice of action from their beliefs and goals. The language provides the basic building blocks to design and implement rational agents. The language elements and features of GOAL allow and facilitate the manipulation of an agent's beliefs and goals and to structure its decision-making. The language provides an intuitive programming framework based on common sense notions and basic practical reasoning."\footnote{The GOAL Programming Language Guide, 2009, 15-05-2015, http://ii.tudelft.nl/trac/goal}}
}

\newglossaryentry{GAMYGDALA}
{
  name=GAMYGDALA,
  description={"GAMYGDALA is an easy to use emotion engine for games. It enables developers to simulate emotions in NPC's. GAMYGDALA can be used in a black-box game-AI independent manner."\footnote{GAMYGDALA: an Emotion Engine for Games Alexandru Popescu, Joost Broekens, and Maarten van Someren (2014). IEEE Transactions on Affective Computing, 5(1), 32-44}}
}

\newglossaryentry{Checkstyle}
{
  name=Checkstyle,
  description={"Checkstyle is a development tool to help programmers write Java code that adheres to a coding standard. It automates the process of checking Java code to spare humans of this boring (but important) task. This makes it ideal for projects that want to enforce a coding standard."\footnote{Checkstyle, 2001, 15-05-2015, http://checkstyle.sourceforge.net}}
}

\newglossaryentry{SEM}
{
  name=Software Engineering Principals,
  description={These are the principals that are used during software engineering, which ensure good overall code. This includes good usage of design patterns, responsibility driven design and a good code architecture}
}

\newglossaryentry{Tygron}
{
  name=Tygron,
  description={"The Tygron engine is a game engine, especially designed to generate and maintain online, multiplayer serious games for spatial development. The software is designed to be used by non-programmers, providing the user a suite of visual development tools in addition to reusable software components. In addition, the Engine uses templates to rapidly set up games."\footnote{Tygron, 2005, 15-05-2015, http://www.tygron.com}}
}

\newglossaryentry{SIG}
{
  name=SIG,
  description={The Software Improvement Group is a company that examines, tests and makes reports about software}
}

\newglossaryentry{SCRUM}
{
  name=SCRUM,
  description={"Scrum is an Agile framework for completing complex projects. Scrum originally was formalized for software development projects, but it works well for any complex, innovative scope of work"\footnote{SCRUM, 2007, 15-05-2015, https://www.scrumalliance.org/why-scrum}}
}